### 2025-07-29 player-evaluation.qmd
20250728 - team quality

- team quality
- role on team
- teammates
- opportunity and usage
    - snap count
    - touches/targets
    - red zone usage

Football is a team sport.
A player is embedded within a broader team context; it is important to consider the strength of their team context insofar as it may support— or detract from—a player's performance.
For instance, for a Quarterback, it is important to consider how strong the pass blocking is from the Offensive Line.
Will they have enough time to throw the ball, or will they be constantly under pressure to be sacked?
It is also important to consider the strength of the pass catchers—the Wide Receivers and Tight Ends.
For a Running Back, it is important to consider how strong the run blocking is from the Offensive Line.
For a Wide Receiver, it is important to consider how strong the pass blocking is, and how strong the Quarterback is.

>>>>

- team quality
    - quality of the team's offense
    - quality of the team's defense
- role on team
- teammates
- opportunity and usage
    - snap count
    - touches/targets
    - red zone usage

Football is a team sport.
A player is embedded within a broader team context; it is important to consider the strength of their team context insofar as it may support— or detract from—a player's performance.
For instance, for a Quarterback, it is important to consider how strong the pass blocking is from the Offensive Line.
Will they have enough time to throw the ball, or will they be constantly under pressure to be sacked?
It is also important to consider the strength of the pass catchers—the Wide Receivers and Tight Ends.
For a Running Back, it is important to consider how strong the run blocking is from the Offensive Line.
For a Wide Receiver, it is important to consider how strong the pass blocking is, and how strong the Quarterback is.
In general, offensive players benefit from being on stronger offenses, so it can make sense to draft players (onto your fantasy team) that are on strong offenses.
In addition, offensive players can also benefit from being on teams with weaker defenses because that may force the offense to score more points.
